%\section{Bibliography\label{sec:bib}}
\begin{thebibliography}{99}
\addcontentsline{toc}{section}{\refname}  
\markboth{\textsc{MLD2P4 User's and Reference Guide}}
         {\textsc{References}}

%\let\refname\relax

%
%\bibitem{PARA04FOREST}
%G.~Bella, S.~Filippone, A.~De Maio, A., Testa, M.: 
%A Simulation Model for Forest Fires.
%In: Dongarra, J., Madsen, K., Wasniewski, J. (eds.):
%Proceedings of PARA~04 Workshop on State of the Art
%in Scientific Computing. Lecture Notes in Computer Science, 3732. Berlin:
%Springer, 2005
%
\bibitem{BREZINA_VANEK}
M.~Brezina, P.~Van{\v e}k,
{\em A Black-Box Iterative Solver Based on a Two-Level Schwarz Method},
Computing, 63, 1999, 233--263.
%
\bibitem{para_04}
A.~Buttari, P.~D'Ambra, D.~di Serafino, S.~Filippone,
{\em Extending PSBLAS to Build Parallel Schwarz Preconditioners},
in , J.~Dongarra, K.~Madsen, J.~Wasniewski, editors,
Proceedings of PARA~04 Workshop on State of the Art
in Scientific Computing, Lecture Notes in Computer Science,
Springer, 2005, 593--602.
%
\bibitem{aaecc_07} 
A.~Buttari, P.~D'Ambra, D.~di~Serafino, S.~Filippone,
{\em 2LEV-D2P4: a package of high-performance preconditioners
for scientific and engineering applications},
Applicable Algebra in Engineering, Communications and Computing, 
18, 3, 2007, 223--239.
%Published online: 13 February 2007, {\tt http://dx.doi.org/10.1007/s00200-007-0035-z}
%
\bibitem{apnum_07}  P.~D'Ambra, S.~Filippone,  D.~di~Serafino,
{\em On the Development of PSBLAS-based Parallel Two-level Schwarz Preconditioners},
Applied Numerical Mathematics, Elsevier Science, 
57, 11-12, 2007, 1181-1196.
%published online 3 February 2007, {\tt
%  http://dx.doi.org/10.1016/j.apnum.2007.01.006}

%% \bibitem{DOUGLAS}
%% R.E.~Bank and C.C.~Douglas,
%% {\em SMMP: Sparse Matrix Multiplication Package}, 
%% Advances in Computational Mathematics, 1993, 1, 127-137.
%% (See also {\tt http://www.mgnet.org/~douglas/ccd-codes.html}) 
%
%
%% \bibitem{CAI_SAAD}
%% X.~C.~Cai and Y.~Saad,
%% {\em Overlapping Domain Decomposition Algorithms for General Sparse Matrices},
%% Numerical Linear Algebra with Applications, 3(3), pp.~221--237, 1996.
%
\bibitem{CAI_SARKIS}
X.~C.~Cai, M.~Sarkis,
{\em A Restricted Additive Schwarz Preconditioner for General Sparse Linear Systems},
SIAM Journal on Scientific Computing, 21, 2, 1999, 792--797.
%
\bibitem{Cai_Widlund_92}
X.~C.~Cai, O.~B.~Widlund,
{\em Domain Decomposition Algorithms for Indefinite Elliptic Problems},
SIAM Journal on Scientific and Statistical Computing, 13, 1, 1992, 243--258.
%
\bibitem{dd1_94}
T.~Chan and T.~Mathew,
{\em Domain Decomposition Algorithms},
in A.~Iserles, editor, Acta Numerica 1994, 61--143.
Cambridge University Press.
%
\bibitem{MLD2P4_TOMS} 
P.~D'Ambra, D.~di~Serafino, S.~Filippone,
\emph{MLD2P4: a Package of Parallel Multilevel
Algebraic Domain Decomposition Preconditioners
in Fortran 95},  ACM Trans. Math. Softw., 37(3), 2010.
%
\bibitem{UMFPACK}
T.A.~Davis, 
{\em Algorithm 832: UMFPACK - an Unsymmetric-pattern Multifrontal
Method with a Column Pre-ordering Strategy},
ACM Transactions on Mathematical Software, 30, 2004, 196--199.
(See also {\tt http://www.cise.ufl.edu/~davis/})
%

\bibitem{MUMPS}
P.R.~Amestoy, C.~Ashcraft, O.~Boiteau, A.~Buttari, J.~L'Excellent, C.~Weisbecker 
{\em Improving multifrontal methods by means of block low-rank representations},
SIAM SISC, volume 37, number 3, pages A1452-A1474.
(See also {\tt http://mumps.enseeiht.fr})
%

\bibitem{SUPERLU}
J.W.~Demmel, S.C.~Eisenstat, J.R.~Gilbert, X.S.~Li and J.W.H.~Liu,
A supernodal approach to sparse partial pivoting,
SIAM Journal on Matrix Analysis and Applications, 20, 3, 1999, 720--755.
%
\bibitem{blas3}
J.~J.~Dongarra, J.~Du Croz, I.~S.~Duff, S.~Hammarling,
\emph{A set of Level 3 Basic Linear Algebra Subprograms},
ACM Transactions on Mathematical Software, 16, 1990, 1--17.
%
\bibitem{blas2}
J.~J.~Dongarra, J.~Du Croz, S.~Hammarling, R.~J.~Hanson,
\emph{An extended set of FORTRAN Basic Linear Algebra Subprograms},
ACM Transactions on Mathematical Software, 14, 1988, 1--17.
%
\bibitem{BLACS}
J.~J.~Dongarra and R.~C.~Whaley,
{\em A User's Guide to the BLACS v.~1.1},
Lapack Working Note 94, Tech.\ Rep.\ UT-CS-95-281, University of
Tennessee, March 1995 (updated May 1997).
%
%\bibitem{sblas_97}
%I.~Duff, M.~Marrone, G.~Radicati and C.~Vittoli,
%{\em Level 3 Basic Linear Algebra Subprograms for Sparse Matrices: 
%a User Level Interface},
%ACM Transactions on Mathematical Software, 23(3), pp.~379--401, 1997.
%
%\bibitem{sblas_02}
%I.~Duff, M.~Heroux and R.~Pozo,
%{\em An Overview of the Sparse Basic Linear
%Algebra Subprograms: the New Standard from the BLAS Technical Forum},
%ACM Transactions on Mathematical Software, 28(2), pp.~239--267, 2002.
%
\bibitem{EFSTATHIOU} 
E.~Efstathiou, J.~G.~Gander,
{\em Why Restricted Additive Schwarz Converges Faster than Additive Schwarz},
BIT Numerical Mathematics, 43, 2003, 945--959.
%
\bibitem{PSBLASGUIDE}
S.~Filippone, A.~Buttari, 
{\em PSBLAS-3.0 User's Guide. A Reference Guide for the Parallel Sparse BLAS Library}, 2012,
available from \texttt{http://www.ce.uniroma2.it/psblas/}.

\bibitem{PSBLAS3}
Salvatore Filippone and Alfredo Buttari.
{\em {Object-Oriented Techniques for Sparse Matrix Computations in Fortran
  2003}.}
ACM Trans. on Math Software, 38(4), 2012.

%
\bibitem{psblas_00}
S.~Filippone, M.~Colajanni, 
{\em PSBLAS: A Library for Parallel Linear Algebra
Computation on Sparse Matrices},
ACM Transactions on Mathematical Software, 26, 4, 2000, 527--550.
%
\bibitem{MPI2}
W.~Gropp, S.~Huss-Lederman, A.~Lumsdaine, E.~Lusk, B.~Nitzberg, W.~Saphir, M.~Snir, 
{\em MPI: The Complete Reference. Volume 2 - The MPI-2 Extensions},
MIT Press, 1998.
%
\bibitem{blas1}
C.~L.~Lawson, R.~J.~Hanson, D.~Kincaid, F.~T.~Krogh,
\emph{Basic Linear Algebra Subprograms for FORTRAN usage},
ACM Transactions on Mathematical Software, 5, 1979, 308--323.
%
\bibitem{SUPERLUDIST}
X.~S.~Li, J.~W.~Demmel, {\em SuperLU\_DIST: A Scalable Distributed-memory
Sparse Direct Solver for Unsymmetric Linear Systems},
ACM Transactions on Mathematical Software, 29, 2, 2003, 110--140.
%
%\bibitem{KIVA3PSBLAS}
%S.~Filippone, P.~D'Ambra, M.~Colajanni,
%{\em Using a Parallel Library of Sparse Linear Algebra in a Fluid Dynamics 
%Applications Code on Linux Clusters},
%in G.~Joubert, A.~Murli, F.~Peters, M.~Vanneschi, editors,
%Parallel Computing - Advances \& Current Issues,
%pp.~441--448, Imperial College Press, 2002. 
%
%\bibitem{METIS}
%Karypis, G. and Kumar, V.,
%{\em {METIS}: Unstructured Graph Partitioning and Sparse Matrix
%  Ordering System}.
%Minneapolis, MN 55455: University of Minnesota, Department of
%  Computer Science, 1995. 
%Internet Address: {\verb|http://www.cs.umn.edu/~karypis|}.
%\bibitem{BLAS1}
%Lawson, C.,  Hanson, R., Kincaid, D. and Krogh, F.,
%   Basic {L}inear {A}lgebra {S}ubprograms for {F}ortran usage,
%{ACM Trans. Math. Softw.} vol.~{5}, 38--329, 1979.
%
%\bibitem{machiels}
%{Machiels, L. and Deville, M.}
%{\em Fortran 90: An entry to object-oriented programming for the solution
%  of partial differential equations.}
%{ACM Trans. Math. Softw.} vol.~{23}, 32--49.
%\bibitem{metcalf}
%{Metcalf, M., Reid, J. and Cohen, M.}
%{\em Fortran 95/2003 explained.}
%{Oxford University Press}, 2004.
%
\bibitem{Saad_book}
Y.~Saad,
\emph{Iterative methods for sparse linear systems}, 2nd edition,
SIAM, 2003

\bibitem{dd2_96}
B.~Smith, P.~Bjorstad, W.~Gropp,
{\em Domain Decomposition: Parallel Multilevel Methods for Elliptic
Partial Differential Equations},
Cambridge University Press, 1996.
%
\bibitem{MPI1}
M.~Snir, S.~Otto, S.~Huss-Lederman, D.~Walker, J.~Dongarra,
{\em MPI: The Complete Reference. Volume 1 - The MPI Core}, second edition,
MIT Press, 1998.
%%
\bibitem{StubenGMD69_99}
K.~St\"{u}ben,
{\em Algebraic Multigrid (AMG): an Introduction with Applications},
in A.~Sch\"{u}ller, U.~Trottenberg, C.~Oosterlee, editors, Multigrid,
Academic Press, 2000.
%
\bibitem{TUMINARO_TONG}
R.~S.~Tuminaro, C.~Tong,
{\em Parallel Smoothed Aggregation Multigrid: Aggregation Strategies on Massively Parallel Machines},
in J. Donnelley, editor, Proceedings of SuperComputing 2000, Dallas, 2000.
%
\bibitem{VANEK_MANDEL_BREZINA}
P.~Van{\v e}k, J.~Mandel and M.~Brezina,
{\em Algebraic Multigrid by Smoothed Aggregation for Second and Fourth Order Elliptic Problems},
Computing, 56, 1996, 179-196.
%

\end{thebibliography}
