\begin{thebibliography}{99}

%
\bibitem{PARA04FOREST}
Bella, G., Filippone, S., De Maio, A., Testa, M.:
A Simulation Model for Forest Fires.
In: Dongarra, J., Madsen, K., Wasniewski, J. (eds.):
Proceedings of PARA~04 Workshop on State of the Art
in Scientific Computing. Lecture Notes in Computer Science, 3732. Berlin:
Springer, 2005
%
\bibitem{aaecc_07} A. Buttari, D. di Serafino, P. D'Ambra, S. Filippone,\newblock
2LEV-D2P4: a package of high-performance preconditioners,\newblock
Applicable Algebra in Engineering, Communications and Computing, 
Volume 18, Number 3, May, 2007, pp.  223-239
%Published online: 13 February 2007, {\tt http://dx.doi.org/10.1007/s00200-007-0035-z}
%
\bibitem{apnum_07}  P. D'Ambra, S. Filippone,  D. Di Serafino\newblock
On the Development of PSBLAS-based Parallel Two-level Schwarz Preconditioners
\newblock
Applied Numerical Mathematics, Elsevier Science, 
Volume 57, Issues 11-12, November-December 2007, Pages 1181-1196.
%published online 3 February 2007, {\tt
%  http://dx.doi.org/10.1016/j.apnum.2007.01.006}

%% \bibitem{DOUGLAS}
%% R.E.~Bank and C.C.~Douglas,
%% {\em SMMP: Sparse Matrix Multiplication Package}, 
%% Advances in Computational Mathematics, 1993, 1, 127-137.
%% (See also {\tt http://www.mgnet.org/~douglas/ccd-codes.html}) 
%
%
\bibitem{para_04}
A.~Buttari, P.~D'Ambra, D.~di Serafino and S.~Filippone,
{\em Extending PSBLAS to Build Parallel Schwarz Preconditioners},
in , J.~Dongarra, K.~Madsen, J.~Wasniewski, editors,
Proceedings of PARA~04 Workshop on State of the Art
in Scientific Computing, pp.~593--602, Lecture Notes in Computer Science,
Springer, 2005.
%
%% \bibitem{CAI_SAAD}
%% X.~C.~Cai and Y.~Saad,
%% {\em Overlapping Domain Decomposition Algorithms for General Sparse Matrices},
%% Numerical Linear Algebra with Applications, 3(3), pp.~221--237, 1996.
%% %
%% \bibitem{CAI_SARKIS}
%% X.C.~Cai and M.~Sarkis,
%% {\em A Restricted Additive Schwarz Preconditioner for General Sparse Linear Systems},
%% SIAM Journal on Scientific Computing, 21(2), pp.~792--797, 1999.
%
\bibitem{Cai_Widlund_92}
X.C.~Cai and O.~B.~Widlund,
{\em Domain Decomposition Algorithms for Indefinite Elliptic Problems},
SIAM Journal on Scientific and Statistical Computing, 13(1), pp.~243--258, 1992.
%
\bibitem{dd1_94}
T.~Chan and T.~Mathew,
{\em Domain Decomposition Algorithms},
in A.~Iserles, editor, Acta Numerica 1994, pp.~61--143, 1994.
Cambridge University Press.
%% %
%% \bibitem{UMFPACK}
%% T.A.~Davis, 
%% {\em Algorithm 832: UMFPACK - an Unsymmetric-pattern Multifrontal
%% Method with a Column Pre-ordering Strategy},
%% ACM Transactions on Mathematical Software, 30, pp.~196--199, 2004.
%% (See also {\tt http://www.cise.ufl.edu/~davis/})
%% %
%% \bibitem{SUPERLU}
%% J.W.~Demmel, S.C.~Eisenstat, J.R.~Gilbert, X.S.~Li and J.W.H.~Liu,
%% A supernodal approach to sparse partial pivoting,
%% SIAM Journal on Matrix Analysis and Applications, 20(3), pp.~720--755, 1999.
%
\bibitem{BLACS}
J.~J.~Dongarra and R.~C.~Whaley,
{\em A User's Guide to the BLACS v.~1.1},
Lapack Working Note 94, Tech.\ Rep.\ UT-CS-95-281, University of
Tennessee, March 1995 (updated May 1997).
%
\bibitem{sblas_97}
I.~Duff, M.~Marrone, G.~Radicati and C.~Vittoli,
{\em Level 3 Basic Linear Algebra Subprograms for Sparse Matrices: 
a User Level Interface},
ACM Transactions on Mathematical Software, 23(3), pp.~379--401, 1997.
%
\bibitem{sblas_02}
I.~Duff, M.~Heroux and R.~Pozo,
{\em An Overview of the Sparse Basic Linear
Algebra Subprograms: the New Standard from the BLAS Technical Forum},
ACM Transactions on Mathematical Software, 28(2), pp.~239--267, 2002.
%
\bibitem{psblas_00}
S.~Filippone and M.~Colajanni, 
{\em PSBLAS: A Library for Parallel Linear Algebra
Computation on Sparse Matrices},
\newblock
ACM Transactions on Mathematical Software, 26(4), pp.~527--550, 2000.
%
\bibitem{KIVA3PSBLAS}
S.~Filippone, P.~D'Ambra, M.~Colajanni,
{\em Using a Parallel Library of Sparse Linear Algebra in a Fluid Dynamics 
Applications Code on Linux Clusters},
in G.~Joubert, A.~Murli, F.~Peters, M.~Vanneschi, editors,
Parallel Computing - Advances \& Current Issues,
pp.~441--448, Imperial College Press, 2002. 
%
\bibitem{METIS}
Karypis, G. and Kumar, V.,
{\em {METIS}: Unstructured Graph Partitioning and Sparse Matrix
  Ordering System}.
Minneapolis, MN 55455: University of Minnesota, Department of
  Computer Science, 1995. 
Internet Address: {\verb|http://www.cs.umn.edu/~karypis|}.
\bibitem{BLAS1}
Lawson, C.,  Hanson, R., Kincaid, D. and Krogh, F.,
   Basic {L}inear {A}lgebra {S}ubprograms for {F}ortran usage,
{ACM Trans. Math. Softw.} vol.~{5}, 38--329, 1979.

\bibitem{machiels}
{Machiels, L. and Deville, M.}
{\em Fortran 90: An entry to object-oriented programming for the solution
  of partial differential equations.}
{ACM Trans. Math. Softw.} vol.~{23}, 32--49.
\bibitem{metcalf}
{Metcalf, M., Reid, J. and Cohen, M.}
{\em Fortran 95/2003 explained.}
{Oxford University Press}, 2004.

\bibitem{dd2_96}
B.~Smith, P.~Bjorstad and W.~Gropp,
{\em Domain Decomposition: Parallel Multilevel Methods for Elliptic
Partial Differential Equations},
Cambridge University Press, 1996.

\bibitem{MPI1}
M.~Snir, S.~Otto, S.~Huss-Lederman, D.~Walker and J.~Dongarra,
{\em MPI: The Complete Reference. Volume 1 - The MPI Core}, second edition,
MIT Press, 1998.
%
\bibitem{BREZINA_VANEK}
M.~Brezina and P.~Van{\v e}k,
{\em A Black-Box Iterative Solver Based on a Two-Level Schwarz Method},
Computing, 1999, 63, 233-263.
%
%
\bibitem{VANEK_MANDEL_BREZINA}
P.~Van{\v e}k, J.~Mandel and M.~Brezina,
{\em Algebraic Multigrid by Smoothed Aggregation for Second and Fourth Order Elliptic Problems},
Computing, 1996, 56, 179-196.
%

\end{thebibliography}